### 2017-09-29 TF-vldb2018/sec-tsimAlg.tex

Given a ball $\ball{[v,r]}$, we calculate the upper bound of $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the current $k$-th result, \ie there is a possibility the for the ball;
Otherwise, we the ball is simply ignored to avoid redundant computations for  team simulation.

>>>>

Given a ball $\ball{[v,r]}$, we compute the density upper bound  $\density{\hat{G}_s}$,
where $\hat{G}_s$ is a subgraph of $\ball{[v,r]}$.
If the bound is larger than the density of the current $k$-th result, \ie there is a possibility the for the ball;
Otherwise, the ball is simply ignored to avoid redundant computations.
